---
title: "Individual_looping_reports"
author: "Ahmir Postell"
format: html
---

# For Each Athlete

### Full Summary

-   total \# of times saluted routine

-   total \# of Events that contributed per year

-   total amount of points earned (this year as well as other years)

-   duration of time on team

-   how average score compares to team average

### Event Summaries (by year)

-   average score per event for each year
-   number of time competed per event for each year
    -   Maybe a rank for how they did among teammates
-   variability per each event for each year
-   distribution visual
-   line plot of score for each event
    -   and progression of average score per year
-   personal best score

```{r}
install.packages("RPostgreSQL")
install.packages("openxlsx")
```
```{r}
# reading in relavent packages
library(RPostgreSQL)
library(openxlsx)
library(tidyverse)
library(dplyr)
library(knitr)
library(rmarkdown)
```

```{r}
# getting data
tryCatch({
    drv <- dbDriver("PostgreSQL")
    print("Connecting to Database…")
    connec <- dbConnect(drv, 
                 dbname = "TribeGym",
                 host = "localhost", 
                 port = 4444,
                 user = "ahmirpostell", 
                 password = "123Ad0gs")
    print("Database Connected!")
    },
    error=function(cond) {
            print("Unable to connect to Database.")
    })
```



```{r}
scores <- dbGetQuery(connec, 
                     "SELECT name, athlete_id, event, score, comp_name, comp_date FROM score
                     LEFT JOIN member
                     ON member.id = score.athlete_id
                     LEFT JOIN competition
                     ON competition.id = score.competition_id")
members <- dbGetQuery(connec,
                      "SELECT * FROM member")
events <- dbGetQuery(connec,
                     "SELECT * FROM apparatus")
```



```{r}
# closing SQL connection
dbDisconnect(connec)
```

```{r}
years <- 2020:2024
#team scores
team_2024 <- scores %>% filter(format(as.POSIXct(scores$comp_date), "%Y") == "2020")

viewing_scores <- scores %>% filter(athlete_id == 1)
viewing_events <- unique(viewing_scores$event)

# saluted routines
routine_count <- nrow(viewing_scores)

# averages
vs_2024 <- viewing_scores %>% filter(format(as.POSIXct(viewing_scores$comp_date), "%Y") == "2024")

avg_2024 <- c()
for (x in events) {
  temp_df <- vs_2024 %>% filter(event == x)
  if (length(temp_df$score) != 0) {
    avg_2024[x] <- mean(temp_df$score)
  }
}
avg_2024



```

```{r}
avg <- function(year, id = NULL) {
  subset <- scores %>% filter(format(as.POSIXct(scores$comp_date), "%Y") == year)
  if (!is.null(id)) {
    subset <- subset %>% filter(athlete_id == id)
  }
  avg <- c()
  for (x in unique(subset$event)) {
  temp_df <- subset %>% filter(event == x)
  if (length(temp_df$score) != 0) {
    avg[x] <- mean(temp_df$score)
    }
  }
  return(avg)
}
```

```{r}
avg("2023", 1)
```



```{r}
sort(unique(format(scores$comp_date, "%Y")))
```

```{r}
all_id <- sort(unique(scores$athlete_id))
all_id
```


```{r}
# Start time
start_time <- Sys.time()

# Set the working directory
dir <- "../../Individual_Reports"
if (!file.exists(dir)) {
  dir.create(dir)
} else {
  # Remove existing files if any
  file.remove(list.files(dir, full.names = TRUE))
}

opts_knit$set(root.dir = dir)

# Run loop to create report for each athlete
for(id in all_id){
  # Rendering pdf
  viewing_scores <- scores %>% filter(athlete_id == id)
  a_name <- viewing_scores$name[1]
  
  # Set the file name of the report
  filename <- paste(a_name, ".pdf", sep = "")
  
  print(paste0("id: ", id))
  print(paste0("filename: ", filename))
  
  # Identify template to create reports; pass parameters to template
  rmarkdown::render(input = "Looping Reports Template 1.Rmd", 
                    output_file = filename,
                    output_dir = dir,
                    params = list(id = id),
                    quiet = TRUE)
}

# End timer
end_time <- Sys.time() - start_time

```

