---
title: "Individual Performance Report"
author: "Ahmir Postell"
output: 
  pdf_document:
    extra_dependencies: ["multicol"]
header-includes:
  - \usepackage{fancyhdr}
  - \usepackage{amsmath}
  - \usepackage{hyperref}
  - \usepackage[table,xcdraw]{xcolor}
  - \usepackage{longtable}
  - \usepackage{graphicx}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
params:
  id: NA
---

```{r}
#| include: false

library(RPostgreSQL)
library(openxlsx)
library(tidyverse)
library(dplyr)
library(knitr)
library(rmarkdown)
library(ggplot2)
library(kableExtra)
```


```{r}
#| include: false

id <- params$id
event_name <- c(
  "FE" = "Floor Exercise",
  "PH" = "Pommel Horse",
  "R" = "Rings",
  "VT" = "Vault",
  "PB" = "Parallel Bars",
  "HB" = "Highbar Bars",
  "AA" = "All Around"
)

```

```{r}
#| include: false
# gathering data
tryCatch({
    drv <- dbDriver("PostgreSQL")
    print("Connecting to Database…")
    connec <- dbConnect(drv, 
                 dbname = "TribeGym",
                 host = "localhost", 
                 port = 4444,
                 user = "ahmirpostell", 
                 password = "123Ad0gs")
    print("Database Connected!")
    },
    error=function(cond) {
            print("Unable to connect to Database.")
    })

scores <- dbGetQuery(connec, 
                     "SELECT name, athlete_id, event, score, comp_name, comp_date FROM score
                     LEFT JOIN member
                     ON member.id = score.athlete_id
                     LEFT JOIN competition
                     ON competition.id = score.competition_id")
members <- dbGetQuery(connec,
                      "SELECT * FROM member")
events <- dbGetQuery(connec,
                     "SELECT * FROM apparatus")

```

```{r}
#| include: false
# closing SQL connection
dbDisconnect(connec)
```

```{r}
#| include: false
# getting relevant data
viewing_scores <- scores %>% filter(athlete_id == id)
viewing_scores$event <- factor(viewing_scores$event, levels = names(event_name))
viewing_scores$year <- format(viewing_scores$comp_date, "%Y")
# constant variables
a_name <- viewing_scores$name[1]
a_routine_count <- nrow(viewing_scores)
a_events <- unique(viewing_scores$event)
a_years <- sort(unique(format(viewing_scores$comp_date, "%Y")))
```


```{r}
#| include: false
# 1st page plot
average_score <- scores %>%
  filter(athlete_id == id) %>%
  group_by(year = format(as.POSIXct(comp_date), "%Y"), event) %>%
  summarise(
    average_score = mean(score, na.rm = TRUE),
    total_routines = n()
  )

if ("AA" %in% a_events) {
  average_score <- average_score %>% filter(event != "AA")
  
}

# Transform the data into long format for ggplot
plot_data <- average_score %>%
  pivot_longer(cols = c("average_score"), 
               names_to = "metric", 
               values_to = "value")
```

```{r}
plot_data
```




```{r}
#| include: false

knitr::opts_chunk$set(echo = FALSE, 
                      tidy.opts = list(width.cutoff = 60), tidy = TRUE)
options(scipen = 999999,
        dplyr.summarise.inform = F)

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(kableExtra))
```

# Performance Report for `r a_name`

This report summarizes the performance data for `r a_name` over the course of his time as a member of William and Mary's Division I Men's Gymnastics Team. `r a_name` has contributed to William and Mary in `r length(a_events)` event(s) over `r length(a_years)` years, saluting a total of `r a_routine_count` routines.

\

\begin{multicols}{2}

Competitive Years\\
```{r echo = FALSE, results = 'asis', eval = TRUE}
for (x in a_years) {
  cat(paste("• ", x, "\\\\"))
}
```

\columnbreak

Competitive Events:\\
```{r echo = FALSE, results = 'asis', eval = TRUE}
for (x in a_events) {
  cat(paste("• ", event_name[x], "\\\\"))
}
```

\end{multicols}

\


```{r echo = FALSE, fig.width=12, fig.height=6}

# Create the line plot
ggplot(plot_data, aes(x = year, y = value, color = event, group = event)) +
  geom_line(size=1) +
  geom_point(size=2) +
  labs(title = "Performance Over Each Year",
       x = "Year",
       y = "Average Score that Year",
       color = "Event") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))



```


```{r}
#| include: false
# helper function
get_ordinal_suffix <- function(n) {
  if (n %% 10 == 0) {
    return("th")
  } else if (n %% 10 == 1 && n %% 100 != 11) {
    return("st")
  } else if (n %% 10 == 2 && n %% 100 != 12) {
    return("nd")
  } else if (n %% 10 == 3 && n %% 100 != 13) {
    return("rd")
  } else {
    return("th")
  }
}

```



```{r echo = FALSE, results = 'asis', eval = TRUE, fig.width=8, fig.height=4}
results <- data.frame(Event = character(), Highest = numeric(), Lowest = numeric(), Average = numeric(), Percentile = character(), stringsAsFactors = FALSE)

for (year in a_years) {
  cat("\\newpage\n\n")
  cat(paste("#", year, "\n\n"))
  
  filtered_scores_year <- scores %>%
    filter(format(as.POSIXct(scores$comp_date), "%Y") == year, athlete_id == id)
  
  cur_events <- unique(filtered_scores_year$event)
  
  for (event in cur_events) {
    filtered_scores_event <- filtered_scores_year %>%
      filter(event == !!event)
    
    this_average <- filtered_scores_event %>%
      summarise(average_score = mean(score, na.rm = TRUE)) %>%
      pull(average_score)
    
    percentile_data <- scores %>%
      filter(format(as.POSIXct(scores$comp_date), "%Y") == year, event == !!event)
    
    ecdf_function <- ecdf(percentile_data$score)
    percentile <- round(ecdf_function(this_average) * 100, digits = 0)

    ordinal_suffix <- get_ordinal_suffix(percentile)
    
    # Add the result to the data frame
    results <- rbind(results, data.frame(Event = event, Highest = max(filtered_scores_event$score), Lowest = min(filtered_scores_event$score), Average = round(mean(filtered_scores_event$score), digits = 2), Percentile = paste0(percentile, ordinal_suffix, " Percentile")))
  }
  
  # Print the results as a table
  table <- kable(results, format = "markdown") %>% 
    kable_styling()
  cat(table, "\n\n")
  
  # Clear the results data frame for the next year
  results <- data.frame(Event = character(), Highest = numeric(), Lowest = numeric(), Average = numeric(), Percentile = character(), stringsAsFactors = FALSE)
  
  athlete_summary <- scores %>%
  filter(format(scores$comp_date, "%Y") == !!year, event %in% cur_events) %>%
  group_by(athlete_id, event,) %>%
  summarise(
    average_score = mean(score, na.rm = TRUE),
    highest_score = max(score, na.rm = TRUE)
  )

scatter_plot <- ggplot(athlete_summary, aes(x = average_score, y = highest_score, color = event)) +
  geom_point(size=2) +
  labs(title = paste0("Scatter Plot of Average vs Highest Scores in ", year),
       x = "Average Score",
       y = "Highest Score") +
  scale_color_discrete(name = "Event") +
  geom_point(data = filter(athlete_summary, athlete_id == id), color = "black", size = 3) +
  guides(color = guide_legend(title = "Event")) + 
  facet_wrap(~ event, scales = 'free')

not_aa <- viewing_scores %>% 
  filter(event != "AA", year == !!year) %>%
  mutate(comp_date = as.Date(comp_date)) %>%
  arrange(comp_date)
line_plot <- ggplot(not_aa, aes(x = comp_date, y = score, color = event)) +
  geom_line() +
  geom_point(size=2) +
  labs(title = paste0("Exact Scores throughout ", year),
       x = "Date",
       y = "Score")

print(scatter_plot)


print(line_plot)
}
```

```{r}
percentile_data
```

